### 2021-01-12 tex/final-presentation.tex
Tweak formatting.
Refactor presentation.

  \begin{frame}{Outline}
    \begin{itemize}
      \item Motivation
      \item Model-Driven Architecture
      \item Low-Code Architecture
      \item Criticisms
      \item Evaluation of Low-Code Tools
      \item Findings \& Future Work
      \item Conclusion
    \end{itemize}
  \end{frame}

@@

  \begin{frame}{Model-Driven Architecture}
    \begin{itemize}
      \item Example: Swagger
        \begin{itemize}
          \item API specification given in OpenAPI format
          \item API client is generated for the specified programming language
          \item support for new languages/frameworks can be added by implementing a new generator
          \item very easy to provide clients for many languages with virtually no development effort
        \end{itemize}
    \end{itemize}
  \end{frame}

  \begin{frame}{Low-Code Architecture}
    \begin{itemize}
      \item provides pre-built application components
      \item graphical user interface for creating both the
            application logic as well as the user interface
      \item typically aimed at end-users rather than developers
    \end{itemize}
  \end{frame}

  \begin{frame}{Criticisms}
    \begin{itemize}
      \item Model-Driven Architecture
        \begin{itemize}
          \item UML diagrams lack details included in the code itself.
          \item “the Code is the design” - Should models be derived from code instead of code from models?
        \end{itemize}
      \item Low-Code Architecture
        \begin{itemize}
          \item Unsuitable for implementing scalable and mission-critical applications.
          \item Increase in unsupported applications built by shadow IT,
                i.e. applications which are not controlled by a company's IT department.
        \end{itemize}
      \item Do these approaches actually make development easier and cheaper?
    \end{itemize}
  \end{frame}

  \begin{frame}{Evaluation of Low-Code Tools}
    \begin{itemize}
      \item Find low-code tools in the following categories:
          \begin{itemize}
            \item open-source
            \item developed by well-known company
            \item developed by unknown company
            \item old/well-established platform
            \item new/unestablished
          \end{itemize}
      \item Set up each tool
      \item Build a test application (TODO List) with each tool
    \end{itemize}
  \end{frame}

@@

  \begin{frame}{Conclusion}
    \begin{itemize}
      \item low-code platforms are a valid alternative to model-driven development
      \item low-code platforms are not as flexible and limited in the ways they can be extended
      \item choice between low-code and model-driven architecture:
        \begin{itemize}
          \item highly dependent on which low-code platform is used, \\
                similar to choosing a programming language or framework for a particular task
          \item highly dependent on the application requirements, \\
                low-code well-suited for management applications (e.g. process management, CRM)
        \end{itemize}
    \end{itemize}
  \end{frame}

>>>>

  \begin{frame}{Outline}
    \begin{itemize}
      \item Motivation
      \item Model-Driven Architecture
      \item Low-Code Architecture
      \item Criticisms
      \item Evaluation of Low-Code Tools
      \item Assessment of Low-Code Tools
      \item Findings \& Future Work
      \item Conclusion
    \end{itemize}
  \end{frame}

@@

  \begin{frame}{Model-Driven Architecture}
    Example: Code Generation using Swagger

    \begin{itemize}
      \item API specification given in OpenAPI format
      \item API client is generated for the specified programming language
      \item support for new languages/frameworks can be added \\
            by implementing a new generator
      \item very easy to provide API clients for many languages with \\
            virtually no development effort
    \end{itemize}
  \end{frame}

  \begin{frame}{Low-Code Architecture}
    \begin{itemize}
      \item provides pre-built application components
      \item graphical user interface for creating both the
            application logic as well as the user interface
      \item typically aimed more at end-users rather than developers
      \item no-code: targeted completely towards end-users
    \end{itemize}
  \end{frame}

  \begin{frame}{Criticisms}
    \begin{itemize}
      \item Model-Driven Architecture
        \begin{itemize}
          \item UML diagrams lack details included in the code itself
          \item “the Code is the design” - Should models be derived from code instead of code from models?
        \end{itemize}
      \item Low-Code Architecture
        \begin{itemize}
          \item unsuitable for implementing scalable and mission-critical applications
          \item increase in unsupported applications built by shadow IT,
                i.e. applications which are not controlled by a company's IT department
        \end{itemize}
      \item Do these approaches actually make development easier and cheaper?
    \end{itemize}
  \end{frame}

  \begin{frame}{Evaluation of Low-Code Tools}
    \begin{itemize}
      \item Find low-code tools in the following categories:
          \begin{itemize}
            \item open-source
            \item developed by well-known company
            \item developed by unknown company
            \item old/well-established platform
            \item new/unestablished
          \end{itemize}
      \item Set up each tool
      \item Build a test application (TODO List) with each tool \\
        \begin{itemize}
          \item add/edit items
          \item mark items as done
        \end{itemize}
    \end{itemize}
  \end{frame}

@@

  \begin{frame}{Conclusion}
    \begin{itemize}
      \item low-code platforms are a valid alternative to model-driven development
      \item low-code platforms are not as flexible and limited in \\
            the ways they can be extended
      \item choice between low-code and model-driven architecture:
        \begin{itemize}
          \item highly dependent on which low-code platform is used, similar to \\
                choosing a programming language or framework for a particular task
          \item highly dependent on the application requirements, \\
                low-code well-suited for management applications \\
                (e.g. process management, CRM)
        \end{itemize}
    \end{itemize}
  \end{frame}
